Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-30 latex/afm-cs-main.tex
Update simulations to cs20ng grating.

The Atomic Force Microscope (AFM) is a powerful instrument capable of imaging
sample surface topography, material characteristics, and other surface
properties, at the nanometer scale. AFMs acquire information about the sample
through a variety of imaging modes, all of which rely on the deflection of the
cantilever caused by the tip-sample interaction force. While the details of each
of the modes are quite different, in general, feedback control is used to hold
the deflection signal constant and information about the property of interest is
inferred from the applied control or the measured dynamics of the cantilever
\cite{Abramovitch:2007gt}. Because of its versatility, spatial resolution, and
ability to image in vacuum, air, and liquid, AFM is widely used in a variety of
disciplines, including physics, biology and materials science
\cite{Dufrene:2017gm,Yang:2017im,Payton:2016hj,Altman:2015ic,Haase:2015eh}

In addition to imaging static samples, AFM is increasingly being applied to
study dynamics in systems with nanometer-scale features
\cite{Yang:2017im,Shibata:2017da,Shibata:2015jd,Ando:2014ja}. The image
acquisition time of conventional AFMs, however, is typically on the order of
seconds to minutes, severely limiting the time-scales that can be explored.
Driven by the need for faster imaging, there continue to be many active research
efforts to overcome this challenge. Since an AFM is fundamentally a mechanical
microscope, many of the approaches to high-speed AFM (HS-AFM) have focused on
modifications to the physical components. These have included the use of small,
fast cantilevers \cite{viani1999fast, braunsmann2010high,Adams:2016hg}, the
development of faster actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm},
as well as the application of advanced controllers
\cite{Rana:2018es,Yong:2015gr,butterworth2010adaptive,salapaka2002high}. By
combining different techniques, there are current generation, high-end
instruments that can image at rates on the order of 1-10 frames/sec
\cite{Ando:2014ja}. However, the fastest rates are achieved only over small scan
ranges and there remain many systems of interest whose dynamics are faster even
than these instruments can achieve. In addition, there is a large installed base
of much slower AFMs that can benefit from alternative approaches to improving
imaging rate.

@@

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.
\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[h!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    % 
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}
     % 
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
    %
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}\\
    % 
    % ------------------------------ Row  2 --------------------------------------------
    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup

>>>>

The Atomic Force Microscope (AFM) is a powerful instrument capable of imaging
sample surface topography, material characteristics, and other surface
properties, with nanometer scale precision. AFMs acquire information about the sample by monitoring the deflection of the cantilever caused by the tip-sample interaction force. In general, 
%AFMs acquire information about the sample
%through a variety of imaging modes, all of which rely on the deflection of the
%cantilever caused by the tip-sample interaction force. While the details of each
%of the modes are quite different, in general, 
feedback control is used to hold
the deflection signal constant and information about the property of interest is
inferred from the applied control or the measured dynamics of the cantilever
\cite{Abramovitch:2007gt}. Because of its versatility, spatial resolution, and
ability to image in vacuum, air, and liquid, AFM is widely used in a variety of
disciplines, including physics, biology and materials science
\cite{Dufrene:2017gm,Yang:2017im,Payton:2016hj,Altman:2015ic,Haase:2015eh}

In addition to imaging static samples, AFM is used to
study dynamics in systems with nanometer-scale features
\cite{Yang:2017im,Shibata:2017da,Shibata:2015jd,Ando:2014ja}. The image
acquisition time of conventional AFMs, however, is typically on the order of
seconds to minutes, severely limiting the time-scales that can be explored.
Driven by the need for faster imaging, there continue to be many active research
efforts to overcome this challenge. Since an AFM is fundamentally a mechanical
microscope, many of the approaches to high-speed AFM (HS-AFM) have focused on
modifications to the physical components. These have included the use of small,
fast cantilevers \cite{viani1999fast, braunsmann2010high,Adams:2016hg}, the
development of faster actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm},
as well as the application of advanced controllers
\cite{Rana:2018es,Yong:2015gr,butterworth2010adaptive,salapaka2002high}. By
combining different techniques, there are current generation, high-end
instruments that can image at rates on the order of 1-10 frames/sec
\cite{Ando:2014ja}. However, the fastest rates are achieved only over small scan
ranges and there remain many systems of interest whose dynamics are faster even
than these instruments can achieve. In addition, there is a large installed base
of much slower AFMs that can benefit from alternative approaches to improving
imaging rate.

@@

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.
\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[h!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    \includesvg[width=0.16\textwidth]{figures/cs20ng_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv_zoom.svg}\\
    % 
    % ------------------------------ Row  2 --------------------------------------------
    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup
